Transfer learning for \'echelle spectroscopy with \texttt{blas\'e}

### 2022-06-22 paper/paper1/ms.tex
Add a second figure of line density to Figure 1, might delete

\documentclass[modern]{aastex631}
\usepackage{hyperref}
\bibliographystyle{aasjournal}
%\turnoffedit
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{censor}
\usepackage{mathtools}
\usepackage{outlines}
\usepackage{amsmath,bm}
\definecolor{belize}{RGB}{41, 128, 185}
\definecolor{peter}{RGB}{52, 152, 219}
\definecolor{nephritis}{RGB}{39, 174, 96}
\definecolor{asbestos}{RGB}{127, 140, 141}
\hypersetup{linkcolor=nephritis,citecolor=belize,filecolor=asbestos,urlcolor=peter}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.5\textwidth]{figures/N_lines_vs_Teff_prom.png}
    \caption{Number of prominent spectral lines versus effective temperature for PHOENIX models truncated to IGRINS (\emph{blue, connected} points) and HPF (\emph{orange, free-standing} points) bandwidths, for different prominence thresholds of $0.02$, $0.01$, and $0.005$.}
    \label{fig_Nlines_vs_teff}
\end{figure}

@@

We compute the residual $\mathsf{R}(\bm{\lambda}_S)$ of native PHOENIX minus cloned model, illustrated in the bottom panel of Figure \ref{fig_cloned_spectrum_demo}. We see an RMS residual of 1.2\%/pixel at native resolution. We identify three main categories of cloning flaws.

@@

Cloning telluric lines suffers from one additional problem.  Telluric lines can be extremely deep, exhibiting almost vanishing transmission with saturated line cores common in-between the atmospheric windows that define the $I$, $J$, $H$, and $K$- bands.  The \texttt{blas\'e} method cannot cope with these saturated lines, and often it treats nearby blended saturated lines as one single line.  The underfit model flounders.

@@

Here we illustrate how \texttt{blas'e} gets altered when applying the logarithmic flux pre-processing step.  First, we compute the natural log of the flux directly on the precomputed synthetic spectrum in its absolute flux scaling and native pixel sampling:

>>>>

\documentclass[modern]{aastex631}
\usepackage{hyperref}
\bibliographystyle{aasjournal}
%\turnoffedit
\usepackage[caption=false]{subfig}
\usepackage{booktabs}
\usepackage{censor}
\usepackage{mathtools}
\usepackage{outlines}
\usepackage{amsmath,bm}
\definecolor{belize}{RGB}{41, 128, 185}
\definecolor{peter}{RGB}{52, 152, 219}
\definecolor{nephritis}{RGB}{39, 174, 96}
\definecolor{asbestos}{RGB}{127, 140, 141}
\hypersetup{linkcolor=asbestos, 
citecolor=belize,filecolor=asbestos,urlcolor=peter}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.45\textwidth]{figures/N_lines_vs_Teff_prom.png}
    \includegraphics[width=0.45\textwidth]{figures/line_density_demo.png}
    \caption{Scaling of prominence and density of spectral lines.  
    \emph{Left:} Number of lines versus effective temperature for PHOENIX models truncated to IGRINS (\textbf{blue, connected} points) and HPF (\emph{red, free-standing} points) bandwidths, for different prominence thresholds of $0.02$, $0.01$, and $0.005$.
    \textbf{Right:} Number of lines per 100 \AA\ wavelength bin for stellar (\emph{blue, upper envelope of steps}) and telluric (\emph{orange, lower envelope of steps}), illustrated for a $T_\mathrm{eff}=4700$~K, $\log{g}=4.5$ PHOENIX model and a $T=290 \mathrm{K}$, relative humidity of 40\% TelFit model.}
    \label{fig_Nlines_vs_teff}
\end{figure}

@@

We compute the residual $\mathsf{R}(\bm{\lambda}_S)$ of native PHOENIX minus cloned model, illustrated in the bottom panel of Figure \ref{fig_cloned_spectrum_demo}. We see an RMS residual of 1.2\%/pixel at native resolution. 
\authorcomment1{Need more prose here.}

We identify three main categories of cloning flaws.

@@

Cloning telluric lines suffers from one additional problem.  Telluric lines can be extremely deep, exhibiting almost vanishing transmission with saturated line cores common in-between the atmospheric windows that define the $I-$, $J-$, $H-$, and $K-$ bands.  The \texttt{blas\'e} method can cope with these saturated lines, but often it treats nearby-and-blended saturated lines as one single line.  This glomming together of lines has little practical effect since few astronomical practitioners can make use of such profoundly saturated data.

@@

Here we illustrate how \texttt{blas\'e} gets altered when applying the logarithmic flux pre-processing step.  First, we compute the natural log of the flux directly on the precomputed synthetic spectrum in its absolute flux scaling and native pixel sampling:
